Variant detection model with improved robustness and accuracy for low-depth targeted next-generation sequencing data

### 2013-12-31 doc/ISMB2014/RVD3.tex
Updated draft and notebook.

>>>>

Massively parallel sequencing data were generated by Next-generation sequencing (NGS) technology to benefit clinical diagnostics and sequencing based phylogenetic analyses. One primary application of NGS is variation detection among related populations and separate novel single-nucleotide variants(SNV) candidates.
Currently SNV are deduced on NGS platform by variants calling algorithms. Typically, SAMtools[XX], Genome Analysis Toolkit (GATK) [XX], VarScan2[XX], and SPLINTER[XX] are all highly used in detecting low-frequency variants. However identifying true SNVs remains challenging because of high false positive rates or high false discovery rate. Another statistical method-RVD, was proposed based on beta-binomial model for ultrasensitive rare single nucleotide variant detection. So based on the RVD hierarchical model we built an improved robustness and accuracy model for low-depth variants detection.
